Determinants of Canadian Politicians' Popularity on Wikipedia.

### 2022-06-24 outputs/paper/paper_working.Rmd
Add 2021 MP election results data

```{r setup, include = FALSE}
# Load Packages ----------------------------------------------------------------
library(tidyverse)
library(knitr)
library(dplyr)
library(ggplot2)
library(here)          # For referencing files in directory
library(kableExtra)    # For formatting tables
library(gridExtra)     # For arranging plots
library(bookdown)      # For cross referencing and citing
library(ggrepel)       # For adding point labels to plots
library(modelsummary)  # For creating summary tables
library(performance)   # For evaluating model performance
library(see)           # For graphing model performance
library(scales)        # For customizing axis scales
library(DiagrammeR)    # For plotting DAGs
library(DiagrammeRsvg) # For plotting DAGs
library(rsvg)          # For plotting DAGs
library(cowplot)       # For arranging plots
library(ggcorrplot)    # For correlation heatmap
library(gtsummary)     # For summary table

@@

>>>>

```{r setup, include = FALSE}
# Load Packages ----------------------------------------------------------------
library(tidyverse)
library(knitr)
library(dplyr)
library(ggplot2)
library(here)          # For referencing files in directory
library(kableExtra)    # For formatting tables
library(gridExtra)     # For arranging plots
library(bookdown)      # For cross referencing and citing
library(ggrepel)       # For adding point labels to plots
library(modelsummary)  # For creating summary tables
library(performance)   # For evaluating model performance
library(see)           # For graphing model performance
library(scales)        # For customizing axis scales
library(DiagrammeR)    # For plotting DAGs
library(DiagrammeRsvg) # For plotting DAGs
library(rsvg)          # For plotting DAGs
library(cowplot)       # For arranging plots
library(ggcorrplot)    # For correlation heatmap
library(gtsummary)     # For summary table
library(janitor)       # For name cleaning

@@

```{r}
# MP Selection -----------------------------------------------------------------
candidates <- read_csv(here("inputs/data/election_candidates.csv"))
candidates <- 
  clean_names(candidates) |>
  mutate(
    full_name = paste(first_name, last_name),
    election_result = as.factor(election_result)
    )

summary(candidates |> select(election_result))

unique(candidates$constituency)

wiki_names <- wiki_data |> filter(is.na(deathyear)) |> select(name)
wiki_names <- wiki_names |>
  mutate(
    name = gsub("\\(.*\\)", "", name),      # Remove bracketed text
    name = gsub("[^a-zA-Z0-9]", "", name),  # Remove special chars
    name = tolower(name)                    # Convert to lowercase
    )

candidates <- candidates |>
  mutate(
    name = full_name,
    name = gsub("\\(.*\\)", "", name),      # Remove bracketed text
    name = gsub("[^a-zA-Z0-9]", "", name),  # Remove special chars
    name = tolower(name)                    # Convert to lowercase
    )

count <- 0
for (name in candidates$full_name) {
  if (name %in% wiki_names$name) {count <- count + 1}
}

print(count)

wiki_data_smol <- wiki_data_cand |> select(name, constituency, party, election_result, matches("views"))

wiki_data_cand <- wiki_data_cand |> select(election_result, page_views)
wiki_data_cand <- wiki_data_cand |> mutate(election_result = as.factor(election_result))
summary(wiki_data_cand)

wiki_data_smol <- wiki_data_smol |>
  group_by(constituency) |>
  mutate(
    most_m6 = as.integer(views_m6 == max(views_m6)),
    most_m7 = as.integer(views_m7 == max(views_m7)),
    most_m8 = as.integer(views_m8 == max(views_m8)),
    most_m9 = as.integer(views_m9 == max(views_m9)),
    most_views = as.integer(page_views == max(page_views))
  ) |>
  ungroup()

wiki_data_smol <- 
  wiki_data_smol |>
  mutate(
    won_most = (election_result == "Re-Elected" & most_views == 1),
    won_least = (election_result != "Re-Elected" & most_views == 1),
    won_most_m9 = (election_result == "Re-Elected" & most_m9 == 1),
    won_least_m9 = (election_result != "Re-Elected" & most_m9 == 1)
  )

wiki_data_smol <- 
  wiki_data_smol |>
  mutate(election_result = as.factor(election_result))

summary(wiki_data_smol)

ggplot(data = wiki_data_smol, aes(x = election_result, y = page_views, fill = election_result)) +
  geom_point()

wiki_names <- 
  wiki_names |> 
  filter(name %in% candidates$full_name)

wiki_data_cand <- 
  wiki_data |>
  filter(name %in% candidates$full_name)

candidates <- candidates |> mutate(name = full_name)

wiki_data_cand <-
  wiki_data_cand |>
  left_join(
    y = candidates,
    by = "name"
  )

wiki_data_cand <- wiki_data_cand |> filter(is.na(deathyear))

single_con <- wiki_data_cand |>
  group_by(constituency) |>
  summarize(
    count = n()
  ) |>
  filter(count > 1)

wiki_data_cand <- 
  wiki_data_cand |> 
  filter(constituency %in% single_con$constituency)

s <- "this is a -, (str here), ' with stuff"
gsub("\\(.*\\)", "", s)
gsub("[^a-zA-Z0-9]", "", s)

election_ts <-
  wiki_data_cand |>
  filter(page_views < 20000) |>
  select(party, election_result, name, starts_with("views")) |>

# Plot
election_ts |>
  ggplot(aes(x = month, y = views, group = name, colour = election_result)) +
  geom_line(alpha = 0.5) +

  # Set axis scales and plot colors
  scale_x_discrete(limits = 1:12, labels = month.abb[1:12]) +
  scale_y_continuous(labels = scales::number) +

  # Set themes
  theme_minimal() +
  theme(legend.position = "top", legend.text = element_text(size = 7))

```
